The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs

### 2021-09-29 src/paper/results/rapid_tests_statistics.tex
Add NRW data on number of performed citizens' rapid tests.

We start with the share of the population doing a rapid test and receiving a positive rapid
test over time by the channel through which the test
was demanded in Figures~\ref{fig:rapid_test_demand_by_channel},
\ref{fig:pos_rapid_tests_by_channel}, respectively. Overall, the share of the population
getting a rapid test on a given day increases from 2\% in mid March to over 10\% by May.
The work rapid tests are a little ragged because of public holidays. For education rapid
tests both vacations (first half of April) as well as the opening of schools in May are
very visible in the rapid test demand. Overall, work tests make up the largest fraction
of rapid tests. The image is very similar for the share of positive tests, except that
the overall number of positive tests starts decreasing in May as rapid test expansion
comes to a halt and cases fall, especially the positive share of private rapid tests
falls as less and less individuals are triggered to seek a rapid test because of a risk
contact in their household.

@@

A similar picture arises, when looking at the false positive rate,
i.e. the share of positive tests that go to people who are not infected.
Figure~\ref{fig:rapid_tests_false_positive_rate} shows that the false
positive rate is very high. On average 60\% to 93\% of positive tests are
received by individuals that are not infected. The false positive rate increases over
time. This is due to the low prevalence of infections in the population, which falls
over time. Again, private rapid tests are an exception with a much lower false
positive rate because those tests are primarily demanded when there is a high likelihood
of being infected. The false negative rate of 0.2\% looks very low. As discussed
above this is deceiving and just a mechanical consequence of a very low prevalence
of the disease and the many rapid tests done by non-infected people.

>>>>

We start with the share of the population doing a rapid test and receiving a positive rapid test
over time by the channel through which the test was demanded in
Figures~\ref{fig:rapid_test_demand_by_channel}, \ref{fig:pos_rapid_tests_by_channel}, respectively.
Overall, the share of the population getting a rapid test on a given day increases from 2\% in mid
March to over 10\% by May. The work rapid tests are a little ragged because of public holidays. For
education rapid tests both vacations (first half of April) as well as the opening of schools in May
are very visible in the rapid test demand. Overall, work tests make up the largest fraction of rapid
tests. The image is very similar for the share of positive tests, except that the overall number of
positive tests starts decreasing in May as rapid test expansion comes to a halt and cases fall,
especially the positive share of private rapid tests falls as less and less individuals are
triggered to seek a rapid test because of a risk contact in their household. The share of private
rapid tests aligns with numbers reported by states on the demand for the free citizen tests
\citep{NRW_rapid_tests}.

@@

A similar picture arises, when looking at the false positive rate, i.e. the share of
positive tests that go to people who are not infected.
Figure~\ref{fig:rapid_tests_false_positive_rate} shows that the false positive rate is
very high. On average 60\% to 93\% of positive tests are received by individuals that
are not infected which is broadly in line with rates later reported in the German media
\citep{SueddeutscheZeitung2021c}. The false positive rate increases over time. This is
due to the low prevalence of infections in the population, which falls over time. Again,
private rapid tests are an exception with a much lower false positive rate because those
tests are primarily demanded when there is a high likelihood of being infected. The
false negative rate of 0.2\% looks very low. As discussed above this is deceiving and
just a mechanical consequence of a very low prevalence of the disease and the many rapid
tests done by non-infected people.
